% The formatting of this CV is based on this tutorial:
% https://latex-tutorial.com/cv-latex-guide/
% and the following:
% https://youtu.be/VjsX4tznW40?si=GKkojwjbw5OHOPHm
% https://youtu.be/o5-BZ7JmYWk?si=duvqfFdG3e6r1sq3
% https://youtu.be/rvgP7IMeUn8?si=Dc0sBV7Wsuw2vnHX

\documentclass{article}

\usepackage{titlesec}
\titlespacing*{\section}{0pt}{5pt}{8pt}
\titlespacing*{\subsection}{0pt}{5pt}{8pt}

\usepackage{titling}
\usepackage[margin=0.7in]{geometry} % set 
\usepackage[colorlinks=true, urlcolor=blue]{hyperref} % enable hyperlinks and specify color
\usepackage{fontawesome} % makes icons for email, github, website, etc
%\usepackage[none]{hyphenat}
%\pagestyle{empty}

%\usepackage{biber}
% Bolding names with publications
% https://tex.stackexchange.com/questions/73136/make-specific-author-bold-using-biblatex

% using titlesec to format sections...
\titleformat{\section}
{\Large\bfseries} %formatting e.g., \lowercase
{} %numbering e.g., \thesection
{0em} % space between title and everything around it
{}[\titlerule] 

\titleformat{\subsection}%[runin} additional argument
{\large\bfseries}
{}
{0em}
{}[\titlerule] 
% reduce space above the section titles


\newcommand{\ts}{\textsuperscript}
\newcommand{\hindent}{\hangindent=10pt}

\begin{document}

\title{Curriculum Vitae}
\author{Able Chow}
\date{}

% using titling to modify title commands
\renewcommand{\maketitle}{
    \begin{center}
        {\huge\bfseries
        \theauthor}\\
        \vspace{0.25em}
        \today\\
        \faEnvelope: ablechow29@gmail.com \\
        % \faGlobe: \website{} \\
        \faGithub: \href{https://github.com/ablechow29}{github.com/ablechow29} \\
        % \faLinkedin: \href {https://www.linkedin.com/in/able-chow-40012b222}{linkedin.com/able-chow}\\
    \end{center}
}

\maketitle

\section{Education}
\newcommand{\education}[4]{
    % name of the sudies
    \noindent \textbf{#1}
    % year on the right side
    \hfill
    \framebox{% year inside a frame box
        \parbox{6em}{%
    \centering \textbf{#2}}} \par
    %new paragraph with the institution in italics
    \noindent {#3} \par
    %description with no hanging and in smaller text
    \vspace*{0.2em}
    \noindent\small #4
    % back to normal size
    \vspace*{0.5em}
\normalsize \par}

\education {M.S., Entomology} {Dec. 2022} 
{Department of Entomology, Louisiana State University} 
{Thesis Title: ``Review of Structural Color in the Genus \textit{Chrysochroa} Dejean, 1833 (Coleoptera: Buprestidae)" (\href{https://repository.lsu.edu/gradschool_theses/5682/}{Link})\\ 
Major Advisor: Dr. Nathan P. Lord \\
Committee: Dr. Bodo Wilts (University of Salzburg, Austria), Dr. Michael Stout (LSU), and Dr. Brant Faircloth (LSU)}

\education {B.S., Entomology} {May. 2018} {Department of Entomology, University of Florida}
{Major Advisor: Dr. Rebecca Baldwin.}

\section{Research Experience}
\newcommand{\Research}[4]{
    % name of the sudies
    \noindent \textbf{#1}
    % year on the right side
    \hfill
    \framebox{% year inside a frame box
        \parbox{6em}{%
    \centering \textbf{#2}}} \par
    %new paragraph with the institution in italics
    \noindent {#3} \par
    %description with no hanging and in smaller text
    \vspace*{0.2em}
    \noindent\small #4
    % back to normal size
    \vspace*{0.5em}
\normalsize \par}

\Research{Graduate Research Assistant} {2018--2022} {Characterizing the structural color of \textit{Chrysochroa} jewel beetles (NSF Funded Project, \#1841704)}{Principal Investigator: Dr. Nathan P. Lord, Louisiana State University}

\Research{Slide Preparator}
{2017--2018}{Developing identification tools for \textit{Anastrepha} fruit fly larva (USDA Funded Project)}
{Supervisor: Dr. Gary Steck, Florida Department of Agriculture and Consumer Services}

\Research{Undergraduate Research Assistant}
{2016--2017}
{Firefly flash pattern analysis project}
{Supervisor: Dr. Marc A. Branham, University of Florida}

\section{Awards and Grants}
\newcommand{\entryB}[4]{
    \noindent
    \begin{minipage}[t]{.73\textwidth}
        \textbf{#1} \\
        \hindent
        \small{#2}
    \end{minipage}
    \begin{minipage}[t]{.12\textwidth}
        \hfill{#3}
    \end{minipage}
    \begin{minipage}[t]{.13\textwidth}
        \hfill{#4}
    \end{minipage}
    \normalsize \par
}

\entryB{The Roussel Scholarship Graduate Student Award in Entomology}
{Louisiana State University}
{\$2000} 
{Sep. 2022} %{Sep. 23, 2022}

\entryB{Graduate Student Research Enhancement Award: Improvement Award}
{The Coleopterists Society}
{\$2000} 
{Jun. 2021} %{Jun. 24, 2021}

\entryB{Graduate Student Association Travel Award}
{Louisiana State University} 
{\$200}
{Oct. 2019} %{Oct. 31, 2019}

\section{Publications}
%\section{Extension Articles}
\newcommand{\BugBiz}[5]{
    \noindent
    \hindent
    {#1} % Authorship string
    {#2}, % Article title
    {#3}, % year
    Bug Biz Series, LSU AgCenter Pub 
    {#4}
    Louisiana State University,
    (\href{#5}{Link}).%url\par
}

\BugBiz{\textbf{\textbf{Chow, A.,}} Huval, F., Mulcahy, M., \& Reagan, T. E.,}
{\textit{Necrophila americana}, American Carrion Beetle (Coleoptera: Silphidae)}
{2021}
{3787}
{https://www.lsuagcenter.com/articles/page1619566292701}

\BugBiz{\textbf{\textbf{Chow, A.,}} Huval, F., Reagan, T. E., \& Carlton, C.,}
{\textit{Photinus pyralis}, Big Dipper Firefly (Coleoptera: Lampyridae)}
{2020}
{3717}
{https://www.lsuagcenter.com/profiles/bneely/articles/page1587050468972}

\BugBiz{\textbf{\textbf{Chow, A.,}} Huval, F., Carlton, C., \& Raegan, T. E.,} 
{\textit{Pyractomena} spp., Spring Fireflies (Coleoptera: Lampyridae)}
{2020}
{3738}
{https://www.lsuagcenter.com/profiles/bneely/articles/page1590080943471}

\section{Contributions to Professional Meetings}
\newcommand{\presentation}[6]{
    \noindent
    \hindent
    \small
    {#1} % Authorship string
    {#2}, % Presentation title
    {#3}, % Conference name
    {#5}, % location
    {#4}. % Presentation date
    (\href{#6}{Link}) %url to online program
    \normalsize \par
}
% Lord, N.P., what is the proper formatting of name acronyms?
% make all presentation titles title case

\subsection{Presentations}
\presentation{\textbf{Chow, A.,} Wilts, B., Lord, N. P., \& Xiao, Y.,}
{Beetles in Golden Skin: Structural Color in \textit{Chrysochroa} Jewel Beetles}
{Society for Integrative and Comparative Biology Annual Meeting}
{Jan. 3, 2023}
{Austin, TX}
{https://sicb.org/wp-content/uploads/2023/04/2023-SICB-Program-R5.pdf}

\presentation{\textbf{Chow, A.,} Wilts, B., Xiao, Y., \& Lord, N. P.,}
{The Spectacular and Peculiar Structural Color of \textit{Chrysochroa} Jewel Beetles (Coleoptera: Buprestidae)} 
{Entomological Society of America (ESA), Entomological Society of Canada (ESC), and Entomological Society of British Colombia (ESBC) Joint Annual Meeting}
{Nov. 16, 2022}
{Vancouver, BC, Canada}
{https://cdmcd.co/B7pd5w}

\presentation{\textbf{Chow, A.,}}
{The Structural Diversity of Multilayer Reflectors in the Jewel Beetle genus \textit{Chrysochroa}}
{Able Chow M.S. Exit Seminar, Department of Entomology, LSU}
{Oct. 7, 2022}
{Baton Rouge, LA}
{https://youtu.be/nBmbMNkQpHo}

\presentation{Canton, R. C., \textbf{Chow, A.,} Moncrieff, A. E., Brumfield, R. T., Lord, N. P., \& Faircloth, B. C.,}
{Evolution of Super-Black Plumage in \textit{Lepidothrix} (Pipridae, Passeriformes)}
{American Ornithological Society and Birds of the Caribbean 2022}
{Jun. 30, 2022}
{San Juan, Puerto Rico}
{https://drive.google.com/file/d/1Jgpf3TN-OHAr3bEgD9NFvzokJmAGDYTp/view?usp=sharing}

\presentation{\textbf{Chow, A.,} \& Lord, N. P.,}
{Taxonomy in Color: Illuminating the Taxonomy of \textit{Chrysochroa} by Understanding Structural Color}
{Society for Integrative and Comparative Biology Annual Meeting} 
{Jan. 6, 2022}
{Virtual}
{https://burkclients.com/sicb/meetings/2022/site/files/2022_SICB_Conference_Program.pdf}

\presentation{\textbf{Chow, A.,} \& Lord, N. P.,}
{Taxonomy in Color, Revision of the Subgenus \textit{Chrooxantha} (Coleoptera: Buprestidae: \textit{Chrysochroa}) Using Morphological and Color Data}
{Entomological Society of America Annual Meeting}
{Nov. 2, 2021}
{Denver, CO}
{https://entomology2021.eventscribe.net/index.asp?presTarget=1760992}

\presentation{\textbf{Chow, A.,} \& Lord, N. P.,}
{Color and Species Delimitation in Jewel Beetles: From Subjective Perception to Objective Definition}
{11\ts{th} Annual LSU Entomology Department Graduate Student Symposium}
{Oct. 22, 2021}
{Baton Rouge, LA}
{https://drive.google.com/file/d/1MhpWrPSVbbUESYt6N1W_Jg5O2Q3pQp1z/view?usp=sharing}

\presentation{\textbf{Chow, A.,} \& Lord, N. P.,}
{Taxonomy in Color: Understanding Structural Color Informs Jewel Beetle Taxonomy}
%what is the proper title????
{Living Light Online Early Career Researcher Conference}
{Sep. 22, 2021}
{Virtual}
{https://drive.google.com/drive/folders/1Cw7rDHG5KeVhH_f5XXtDSGHHVbAQ9A5N?usp=drive_link}

\presentation{\textbf{Chow, A.,} \& Lord, N. P.,}
{Jewels of Iridescence: Mechanisms of Structural Color and its Significance in Insect Systematics}
{Jan. 3--Feb. 28 2021}
{Society for Integrative and Comparative Biology Annual Meeting} {Virtual}
{https://sicb.org/wp-content/uploads/2021/07/2021-SICB-Program-Book.pdf}

\presentation{\textbf{Chow, A.,} \& Lord, N. P.,}
{Jewels of iridescence: Mechanisms of structural color and implications for taxonomy}
{Entomological Society of America Annual Meeting}
{Nov. 19, 2019}
{St. Louis, MO}
{https://www.entsoc.org/sites/default/files/files/Annual\%20Meeting/2019\%20ESA\%20Annual\%20Meeting-Program-web.pdf}

\presentation{\textbf{Chow, A.,} \& Lord, N. P.,}
{When Color Science Meets Taxonomy: Revision of Subgenus \textit{Chrooxantha} Hołyński,2009}
{10\ts{th} Annual LSU Entomology Department Graduate Student Symposium}
{Oct. 9, 2019}
{Baton Rouge, LA}
{https://drive.google.com/file/d/1ZViTaYaxf5ADqvz2CkGRrdrPQo72N4lX/view?usp=sharing}

\presentation{\textbf{Chow, A.,} \& Lord, N. P.,}
{Iridescent Characters: a Taxonomic Revision of Subgenus \textit{Chrooxantha} (Coleoptera: Buprestidae: \textit{Chrysochroa})}
{LSU Department of Entomology Seminar}
{Sep. 20, 2019}
{Baton Rouge, LA}
{https://drive.google.com/file/d/17Uy-8B0jXyXhiPVohnR0msqg-Do9Diof/view?usp=sharing}

\subsection{Posters}
\presentation{\textbf{Chow, A.,} \& Lord, N. P.,}
{The Physics, Biology, and Evolution of Cuticular Iridescence in Jewel Beetles}
{9\ts{th} Annual LSU Entomology Department Graduate Student Symposium}
{Oct. 18, 2018}
{Baton Rouge, LA}
{https://drive.google.com/file/d/1vaKRlffkIMk2d7JBE3QfCNgHwQnY4m3X/view?usp=sharing}

\presentation{\textbf{Chow, A.,} Keller, O., Ivie, M., \& Branham, M. A.,}
{Developing a Data Pipeline (workflow) to Digitally Record and Analyze Firefly Flash Patterns}
{International Firefly Symposium}
{Apr. 25--26, 2017}
{Taipei, Taiwan}
{https://static1.squarespace.com/static/59028899b3db2bade49af818/t/59b2d35149fc2b50d078b3d1/1504891730888/Proceedings+of+2017+IFS.pdf}

\presentation{\textbf{Chow, A.,} Keller, O., Ivie, M., \& Branham, M. A.,}
{Developing a Data Pipeline (workflow) to Digitally Record and Analyze Firefly Flash Patterns}
{Entomological Society of America Southeastern Branch Conference}
{Mar. 14, 2017}
{Memphis, TN}
{https://www.entsoc.org/sites/default/files/files/2017_SEB_Program_Book.pdf}


\section{Exhibitions}

\newcommand{\exhibition}[4]{
    \noindent
    \hindent
    \small
    \textbf{#1} %what is it?
    {#2}, % Detail and Institution
    {#3}, % Conference name
    {#4} % location
    \normalsize \par
}

% email Dr. 
\exhibition{Contributor of \textit{Iridescence: Interdisciplinary Inspiration}}
{Capsule exhibition of larger Louisiana Art \&Science Museum \textit{Iridescence} exhibition, highlighting art and science collaboration}
{Mar. 2--16, 2022}
{Boyce Gallery at the College of Art \& Design, Louisiana State University.}

\exhibition {Contributor of \textit{Iridescence}:}
{Featured exhibition at the Louisiana Art \& Science Museum, Baton Rouge.} 
{Jul. 17, 2021--Jul. 31, 2022}
{This exhibition features the scientific works of Dr. Nathan Lord and his graduate students Able Chow and Sierra Weir, invited works from renowned artists, and a juried competition. \href{https://www.exploreiridescence.com/}{(Link)}}

\section{Training and Skill}
\subsection{Training and Workshop Attended}
%\section{Training and Workshop Attended}
\newcommand{\train}[4]{
    \noindent
    \hindent
    \textbf{#1}\\ % training subject
    {#2}, % Institution
    {#3}, % Trainers
    \small{#4}. % Date
    \par\normalsize
}

\train{SEM specimen preparation and scope operation training}
{LSU Shared Instrument Facilities}
{Dr. Yang Mu \& Dr. Dongmei Cao}
{Jan. 26--Feb. 1, 2021}

\train{TEM specimen preparation and scope operation training}
{Georgia Microscopy, University of Georgia}
{Dr. John Shields \& Ms. Mary Ard}
{Oct. 28--30, 2020}

\subsection{Student Training Provided}
%\section{Student Training Provided}
\textbf{Imaging System Workshop for Entomology Graduate Students}, 
\small{Jan. 13 \& Apr. 6, 2022.}\normalsize

\subsection{Other Skills}
\newcommand{\skills}[2]{
    \noindent
    \begin{minipage}[t]{.50\textwidth}
    \textbf{#1}:
    \end{minipage}
    \begin{minipage}[t]{.45\textwidth}
    {#2}\hfill
    \end{minipage}
    \normalsize \par
}

\skills{Programming Languages}{\LaTeX, R, BASH}
\skills{Integrated Development Environment}{Vim, Neovim, R Studio}

\section{Teaching Assistantship}
\newcommand{\TA}[5]{
    \noindent
    \hindent
    \textbf{#1}, %course
    {#2}, % Institution
    {#3}, % Trainers
    {#4}.\\ % Date
    \small{#5}. % footnotes
    \normalsize\par
}

\TA{General Entomology (ENTM 7001)}
{Department of Entomology}
{Louisiana State University}
{Fall 2021}
{2 lectures given: Insect Behavior and Insect Morphology}

\section{Collections Research}
\newcommand{\entryA}[3]{
    \noindent
    \begin{minipage}[t]{.73\textwidth}
    \textbf{#1}
    \small{#2}
    \end{minipage}
    \begin{minipage}[t]{.25\textwidth}
    \hfill{#3}
    \end{minipage}
    \normalsize \par
}

\entryA{Texas A\&M University Insect Collection}{College Station, Texas}
{Sep. 17--18, 2020}

\entryA{Museum National d’Histoire Naturelle} 
{Paris, France}
{Oct. 13--20, 2019}

\entryA{National Museum}{Prague, Czech Republic}{Oct. 3--12, 2019}

\entryA{California State Arthropod Collection}{Sacramento, California}{Jul. 28--Aug. 3, 2019}

\entryA{California Academy of Sciences}{San Francisco, California}{Jul. 24--27, 2019}

\section{Conference Participation}
\newcommand{\conference}[3]{
    \noindent
    \hindent
    \small
    \textbf{#1}, % Conference name
    {#3}, % location
    {#2}. % Conference date
    \normalsize \par
}

\conference{Society for Integrative and Comparative Biology Annual Meeting}
{Jan. 3--6, 2023}
{Austin, TX}

\conference{ESA, ESC, and ESBC Joint Annual Meeting}
{Nov. 13--16, 2022}
{Vancouver, BC, Canada}

\conference{Society for Integrative and Comparative Biology Annual Meeting}
{Jan. 14--Mar. 31, 2022}
{Virtual}

\conference{Entomological Society of America Annual Meeting}
{Oct. 31--Nov. 3, 2021}
{Denver, CO}

\conference{11\ts{th} Annual LSU Entomology Department Graduate Student Symposium}
{Oct. 22, 2021}
{Baton Rouge, LA}

\conference{Living Light Online Early Career Researcher Conference}
{Sep. 22--23, 2021}
{Virtual}

\conference{Society for Integrative and Comparative Biology Annual Meeting}
{Jan. 3--Feb. 28, 2021}
{Virtual}

\conference{Entomological Society of America Annual Meeting }
{Nov. 17--20, 2019}
{St. Louis, MO}

\conference{10\ts{th} Annual LSU Entomology Department Graduate Student Symposium}
{Oct. 25, 2019}
{Baton Rouge, LA}

\conference{ESA, ESC, and ESBC Joint Annual Meeting}
{Nov. 13--16, 2018}
{Vancouver, BC, Canada}

\conference{9\ts{th} Annual LSU Entomology Department Graduate Student Symposium. }
{Oct. 15, 2018}
{Baton Rouge, LA}

\conference{Entomological Society of America Annual Meeting}
{Nov. 5--8, 2017}
{Denver, CO}

\conference{International Firefly Symposium}
{Apr. 24--26, 2017}
{Taipei, Taiwan}

\conference{Entomological Society of America Southeastern Branch Conference}
{Mar. 12--15, 2017}
{Memphis, TN}


\section{Outreach and Services}
\newcommand{\outreach}[5]{
    \noindent
    \normalsize
    \textbf{#1} % Role
    {#2}, % Event
    \small
    {#3}, % location
    {#4}. % date
    \normalsize\par
}

\outreach{Volunteer}
{for Bioblitz 2022 at the BREC Forest Community Park}
{Baton Rouge, Louisiana}
{Apr. 2022}

\outreach{Volunteer}
{for AgMagic 2022, at the Parker Coliseum in LSU}
{Baton Rouge, LA}
{Mar. 2022}

\outreach{Guest educator}
{for BREC Zoo Children’s Summer Camp}
{Baton Rouge, LA}
{Jul. 2021}

\outreach{Volunteer}
{for BREC Bluebonnet Children’s Summer Camp}
{Baton Rouge, LA}
{Jun. 2021}

\outreach{Assisted}
{in producing the online format of 4-H University Insect Identification Contest}
{Baton Rouge, LA}
{Jun. 2020}

\outreach{Volunteer}
{for Night at the Museum, at the Louisiana State Arthropod Museum}
{Baton Rouge, LA}
{Sep. 2019}

\outreach{Volunteer}
{for AgMagic at the Parker Coliseum in LSU}
{Baton Rouge, LA}
{Apr. 2019}

\outreach{Volunteer}
{for UF Department of Entomology outreach booth at Florida State Fair}
{Tampa, FL}
{Feb. 2017}

\outreach{Volunteer}
{for UF Department of Entomology outreach booth at Florida State Fair}
{Tampa, FL}
{2015}

\section{References}
\newcommand{\References}[5]{
    \noindent
    \begin{minipage}[t]{.25\textwidth}
    \textbf{#1} % Name
    \end{minipage}
    \begin{minipage}[t]{.70\textwidth}
    \noindent
    \small
    {#2}, % Position
    {#3}, % Institution
    Email: {#4} % year
    \end{minipage}
    \normalsize\par
}

% Dr. Bodo Wilts, Professor of Materials Physics, Paris London Universität Salzburg, Email: bodo.wilts@plus.ac.at
% Fix the spacing between Dr. ...

\References{Dr. Christopher Carlton}
{Entomology Diagnostician, Louisiana State University}
{Director Emeritus, Louisiana State Arthropod Museum}
{ccarlt@lsu.edu}

\References{Ms. Victoria Bayless}
{Curator}
{Louisiana State Arthropod Museum}
{vbayless@agcenter.lsu.edu}

\References{Dr. Ilgoo Kang}
{Assistant Professor}
{Kyungpook National University}
{ikang@knu.ac.kr}

\References{Dr. Gary Steck}
{Taxonomic Entomologist and Curator (Diptera)}
{Florida Department of Agriculture and Consumer Services}
{Gary.Steck@freshfromflorida.com}

\References{Dr. Marc Branham}
{Associate Professor}
{University of Florida}
{marcbran@ufl.edu}
 
\end{document}

\subsection{Field Collecting}
\newcommand{\field}[4]{
    \begin{minipage}[t]{.73\textwidth}
    \textbf{#1}\\ %location
    \small{#2} %methods
    \small{#3} % for what
    \end{minipage}
    \begin{minipage}[t]{.25\textwidth}
    \hfill\small{#4} % date
    \end{minipage}
    \normalsize \par
}

\field
{Idlewilde Research Station, Baton Rouge, LA}
{Louisiana State Arthropod Collection}
{Malaise trap, light trap}

%{May. 29, 2019--Jun. 22, 2020}
{Rosedale County, Baton Rouge, LA}

{Insect Taxonomy Class (ENTM 4005)}
{Idlewilde Research Station, Baton Rouge, LA}{Spring semesters, 2019--2022}
{Malaise trap, light trap}


